---
title: "study1b_analysis"
author: "Kelsey Neuenswander"
date: '2022-11-22'
output: html_document
---

**Load Packages**
```{r}
library(ggplot2) # for data visualizing
library(dplyr) # for data cleaning
library(mediation) # for mediational analysis
```

**Load Data**
```{r}
data <- read.csv('study1b_data.csv')
```


**Filter out participants who do not pass attention check**
```{r}
nrow(data)
data <- data %>% filter(attention == 4)
nrow(data)
```

Sample goes from N = 120 to N= 106. Lose 14 participants.

**Demographics**

Sex
```{r}
table(data$gender) # 1 = male, 2 = female, 3 = other
```

Race
```{r}
table(data$race) # 1 = white, 2 = hispanic, 3 = black, 4 = asian, 10 = native american, 16 = other
```

Age
```{r}
stat.desc(data$age)
```


**Create aggregate breadwinning and caregiving rank columns**
```{r}
bread <- data %>% dplyr::select('rank_1', 'rank_2', 'rank_3') %>%
  rowMeans()

care <- data %>% dplyr::select('rank_4','rank_5','rank_6') %>%
  rowMeans()

data <- data %>% mutate(breadwinning = bread,
                        caregiving = care)
```

**Reverse score necessary EGA items**
```{r}
# 2-7, 10-11
data <- data %>% mutate(EGA_2_r = 8 - EGA_2_1,
                        EGA_3_r = 8 - EGA_3_1,
                        EGA_4_r = 8 - EGA_4_1,
                        EGA_5_r = 8 - EGA_5_1,
                        EGA_6_r = 8 - EGA_6_1,
                        EGA_7_r = 8 - EGA_7_1,
                        EGA_10_r = 8 - EGA_10_1,
                        EGA_11_r = 8 - EGA_11_1)
```

**Create new EGA score column**
```{r}
EGA <- data %>% dplyr::select('EGA_1_1','EGA_2_r','EGA_3_r','EGA_4_r','EGA_5_r','EGA_6_r','EGA_7_r','EGA_8_1','EGA_9_1','EGA_10_r','EGA_11_r') %>%
  rowSums()

data <- data %>% mutate(EGA_score = EGA)
```

**Compare expected breadwinning priority between tuesday and saturday dads**
```{r}
# t-test
bread_model <- lm(breadwinning ~ condition, data=data)
summary(bread_model)


# group means
bread_means <- data %>% group_by(condition) %>%
  summarise(mean = mean(breadwinning),
            sd = sd(breadwinning),
            n = n(),
            se = sd(breadwinning)/sqrt(n()))
bread_means
```

**Run mediational analyses for breadwinning**
```{r}
EGA.model <- lm(breadwinning ~ EGA_score, data=data)
fit.mediator <- lm(EGA_score ~ condition, data=data)
fit.dv <- lm(breadwinning ~ condition + EGA_score, data=data)

bread_mediation = mediate(fit.mediator, fit.dv, treat='condition', mediator='EGA_score', boot=T)

summary(EGA.model)
summary(fit.mediator)
summary(bread_mediation)
```


**Compare expected caregiving priority between tuesday and saturday dads**
```{r}
# t-test
care_model <- lm(caregiving ~ condition, data=data)
summary(care_model)


# group means
care_means <- data %>% group_by(condition) %>%
  summarise(mean = mean(caregiving),
            sd = sd(caregiving),
            n = n(),
            se = sd(caregiving)/sqrt(n()))
care_means
```

**Run mediational analyses for caregiving**
```{r}
EGA.model.care <- lm(caregiving ~ EGA_score, data=data)
fit.mediator.care <- lm(EGA_score ~ condition, data=data)
fit.dv.care <- lm(caregiving ~ condition + EGA_score, data=data)

care_mediation = mediate(fit.mediator.care, fit.dv.care, treat='condition', mediator='EGA_score', boot=T)

summary(EGA.model.care)
summary(fit.mediator)
summary(care_mediation)
```